R Notebook

### 2020-04-22 Prep_code/nat_stories_prep.Rmd
label when words are multi-token

grnn_translator <- read_delim("ns_tokens_trans.txt", delim="\t", col_names=c("Item","Word_In_Sentence_Num", "Word","token"), col_types=c(col_character(),col_integer(), col_character(),col_character())) %>% 
  mutate(num=row_number()) %>% 
  left_join(grnn, by="num") %>% 
  mutate(grnn_surp=ifelse(model_token==token & grnn_surp>0, grnn_surp, NA)) %>% 
  select(-model_token, -num) %>% 
  separate(Item, into=c("Story_Num","Sentence_Num"), convert=T) %>% 
  left_join(labelled, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word")) %>% 
  group_by(Story_Num, Sentence_Num,Word_In_Sentence_Num,Word,Word_In_Story_Num) %>% 
  summarize(grnn_surp=sum(grnn_surp))

@@

ngram_translator <- read_delim("ns_lower_trans.txt", delim="\t", col_names=c("Item","Word_In_Sentence_Num", "Word","token"), col_types=c(col_character(),col_integer(), col_character(),col_character())) %>% 
  mutate(num=row_number()) %>% 
  left_join(ngram, by="num") %>% 
  mutate(ngram_surp=ifelse(model_token==token & ngram_surp>0, ngram_surp, NA)) %>% 
  select(-model_token, -num, -sentence_no, -token_no) %>% 
  separate(Item, into=c("Story_Num","Sentence_Num"), convert=T) %>% 
  left_join(labelled, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word")) %>% 
  group_by(Story_Num, Sentence_Num,Word_In_Sentence_Num,Word,Word_In_Story_Num) %>% 
  summarize(ngram_surp=sum(ngram_surp))
```

@@

txl_translator <- read_delim("ns_tokens_moses_trans.txt", delim="\t", 
                             col_names=c("Item","Word_In_Sentence_Num", "Word","token"), 
                             col_types=c(col_character(),col_integer(), col_character(),col_character())) %>% 
  mutate(num=row_number()) %>% 
  left_join(txl, by="num") %>% 
  mutate(txl_surp=ifelse(model_token==token & txl_surp, txl_surp, NA)) %>% 
  select(-model_token, -num) %>% 
  separate(Item, into=c("Story_Num","Sentence_Num"), convert=T) %>% 
  left_join(labelled, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word")) %>% 
  group_by(Story_Num, Sentence_Num,Word_In_Sentence_Num,Word,Word_In_Story_Num) %>% 
  summarize(txl_surp=sum(txl_surp))
```

>>>>

grnn_translator <- read_delim("ns_tokens_trans.txt", delim="\t", col_names=c("Item","Word_In_Sentence_Num", "Word","token"), col_types=c(col_character(),col_integer(), col_character(),col_character())) %>% 
  mutate(num=row_number()) %>% 
  left_join(grnn, by="num") %>% 
  mutate(grnn_surp=ifelse(model_token==token & grnn_surp>0, grnn_surp, NA)) %>% 
  select(-model_token, -num) %>% 
  separate(Item, into=c("Story_Num","Sentence_Num"), convert=T) %>% 
  left_join(labelled, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word")) %>% 
  group_by(Story_Num, Sentence_Num,Word_In_Sentence_Num,Word,Word_In_Story_Num) %>% 
  summarize(grnn_surp=sum(grnn_surp),
            grnn_token_count=n())

@@

ngram_translator <- read_delim("ns_lower_trans.txt", delim="\t", col_names=c("Item","Word_In_Sentence_Num", "Word","token"), col_types=c(col_character(),col_integer(), col_character(),col_character())) %>% 
  mutate(num=row_number()) %>% 
  left_join(ngram, by="num") %>% 
  mutate(ngram_surp=ifelse(model_token==token & ngram_surp>0, ngram_surp, NA)) %>% 
  select(-model_token, -num, -sentence_no, -token_no) %>% 
  separate(Item, into=c("Story_Num","Sentence_Num"), convert=T) %>% 
  left_join(labelled, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word")) %>% 
  group_by(Story_Num, Sentence_Num,Word_In_Sentence_Num,Word,Word_In_Story_Num) %>% 
  summarize(ngram_surp=sum(ngram_surp),
            ngram_token_count=n())
```

@@

txl_translator <- read_delim("ns_tokens_moses_trans.txt", delim="\t", 
                             col_names=c("Item","Word_In_Sentence_Num", "Word","token"), 
                             col_types=c(col_character(),col_integer(), col_character(),col_character())) %>% 
  mutate(num=row_number()) %>% 
  left_join(txl, by="num") %>% 
  mutate(txl_surp=ifelse(model_token==token & txl_surp, txl_surp, NA)) %>% 
  select(-model_token, -num) %>% 
  separate(Item, into=c("Story_Num","Sentence_Num"), convert=T) %>% 
  left_join(labelled, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word")) %>% 
  group_by(Story_Num, Sentence_Num,Word_In_Sentence_Num,Word,Word_In_Story_Num) %>% 
  summarize(txl_surp=sum(txl_surp),
            txl_token_count=n())
```
